Dismal Code: Studying the Evolution of Security Bugs

### 2013-02-07 docs/msr.tex
minor fixes

\begin{table}
\centering
\caption{Bug categorisation according to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file \\
Internationalisation & Indicates the use of non-localized methods \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Security & Contains two subcategories, namely: {\it Security} and {\it
Malicious Code}. Involves code that could lead to security breach. \\
\hline
\end{tabular}
\end{table}

@@

There are noumerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions. The key idea behind this concept is
similar to ours: the combination of information like bug decriptions,
documentation and others with the information retrieved from either the source
or object code of a project version.

@@

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,~\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analyzing the project's
Bugzilla. Their research showed that security bugs require more experienced developers
to be fixed. In addittion, security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analyzed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.

>>>>

\begin{table}
\centering
\caption{Bug categorisation according to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalisation & Indicates the use of non-localized methods. \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Security & Contains two subcategories, namely: {\it Security} and {\it
Malicious Code}. Involves code that could lead to security breach. \\
\hline
\end{tabular}
\end{table}

@@

There are numerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions. The key idea behind this concept is
similar to ours: the combination of information like bug decriptions,
documentation and others with the information retrieved from either the source
or object code of a project version.

@@

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,~\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analyzing the project's
Bugzilla. Their research showed that security bugs require more experienced developers
to be fixed. In addittion, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analyzed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.
